---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# slackthreads

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R-win build status](https://github.com/yonicd/slackthreads/workflows/R-win/badge.svg)](https://github.com/yonicd/slackthreads)
[![R-mac build status](https://github.com/yonicd/slackthreads/workflows/R-mac/badge.svg)](https://github.com/yonicd/slackthreads)
[![R-linux build status](https://github.com/yonicd/slackthreads/workflows/R-linux/badge.svg)](https://github.com/yonicd/slackthreads)
[![Codecov test coverage](https://codecov.io/gh/yonicd/slackthreads/branch/master/graph/badge.svg)](https://codecov.io/gh/yonicd/slackthreads?branch=master)
<!-- badges: end -->

`slackthreads` is a part of `slackverse`

```{r,echo = FALSE, eval = TRUE}
pkgs <- sprintf('slack%s',c('calls','teams','posts','blocks','threads','reprex'))

badges <- sprintf('%s<br>[![](https://github.com/yonicd/%s/workflows/R-mac/badge.svg)](https://github.com/yonicd/%s)',pkgs,pkgs,pkgs)

names(badges) <- pkgs

```

||||
|:-:|:-:|:-:|
||`r badges[pkgs[1]]`<br>`r emo::ji('down_left_arrow')``r emo::ji('down_arrow')``r emo::ji('down_right_arrow')`||
|`r badges[pkgs[5]]`|`r badges[pkgs[2]]`<br>`r emo::ji('left_arrow')``r emo::ji('down_right_arrow')`|`r badges[pkgs[3]]`<br>`r emo::ji('down_arrow')`|
|||`r badges[pkgs[4]]`<br>`r emo::ji('down_arrow')`|
|||`r badges[pkgs[6]]`|

The goal of `slackthreads` is to interact with the Slack API to retrieve and interrogate team conversations.

## Installation

``` r
remotes::install_github("yonicd/slackthreads")
```

## In the Tin

  - Fetch messages from conversations
  - Fetch replies in slackthreads to the messages in the conversations

## Example Using [R4DS Slack](https://www.rfordatasci.com/)

```{r}
library(slackteams)
library(slackthreads)

```
 
### Load the Team 
```{r}
slackteams::load_teams()
slackteams::activate_team('r4ds')
```
 
### Retrieve Team Channels 
 
```{r}
chnls <- slackteams::get_team_channels()

 # r4ds has channels to ask questions in
question_channels <- sort(grep('^help',chnls$name[chnls$is_channel],value = TRUE))

question_channels
```
 
### Retrieve Conversations 

This will retrieve the last 20 messages from the "help-1-explore_wrangle" channel.

```{r}
  
convos <- slackthreads::conversations(channel = 'help-1-explore_wrangle', limit = 20, max_results = 20)

```
 
Check that request was returned ok and that up to 20 were returned. 
 
```{r}
length(convos)
```

There are the following replies to the first message

```{r}
convos[[1]]$reply_count
```

