---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# threads

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of threads is to interact with the Slack API to retrieve and interrogate team conversations.

## Installation

``` r
remotes::install_github("yonicd/threads")
```

## In the Tin

  - Slack API GET for [conversation.history](https://api.slack.com/methods/conversations.history)
  - Slack API GET for [conversation.replies](https://api.slack.com/methods/conversations.replies)
  - Pagination Methods for both
  
More to come ....

## Example Using [R4DS Slack](https://www.rfordatasci.com/)

```{r}
library(slackteams)
library(threads)

```
 
### Load the Team 
```{r}
slackteams::load_teams()
slackteams::activate_team('r4ds')

```
 
### Retrieve Team Channels 
 
```{r}
chnls <- slackteams::get_team_channels()

 # r4ds has channels to ask questions in
question_channels <- sort(grep('^[1-9]',chnls$name[chnls$is_channel],value = TRUE))

question_channels
```
 
### Retrieve Conversations 

This will GET the first 20 messages from each channel

```{r}

question_channels <- setNames(question_channels,question_channels)

convos <- lapply(question_channels,function(chnl){
  threads::get_conversations(limit = 20, channel = chnl)
})

```
 
Check that request was returned ok and that up to 20 were returned. 
 
```{r}
convos[[1]]$ok
length(convos[[1]]$messages)

```
 
### Pagination 
 
We now use that initial object to retrieve the rest of the channel messages using pagination 
 
```{r}
convo_paginate <- threads::paginate(convos[[1]],limit = 100)
```

This will return a list of requests where the first element in the root request that returned 20 messages and the subsequent ones contain up to 100 messages

```{r}
lapply(convo_paginate,function(x) length(x$messages))
```

### Messages Replies (Threads)

How many replies were there to this message

```{r}
convos[[1]]$messages[[1]]$reply_count
```

Retrieve the reply.

The first element will be the parent message and the subsequent ones are the messages in the thread.

```{r}
reply <- threads::get_replies(convos[[1]]$messages[[1]]$ts,channel = names(convos)[1])

```
 
Check that request was returned ok and how many messages where returned
 
```{r}
reply$ok
length(reply$messages)
```
